From DSL to HPC Component-Based Runtime:\\ A Multi-Stencil DSL Case Study

### 2015-09-25 WOLFHPC15/article/evaluation.tex
copyright ACM template + corrections Helene

Figure~\ref{fig:exectime} illustrates the execution time for each step of the MSC transformation for an overall execution time of ten seconds. Execution times have been computed on a laptop with a bi-core Intel Core i5 1.4~GHz, and 8~GB of DDR3. 
One can notice that the transformation of $\Gamma_{dep}$ to a minimal series-parallel graph is the longest step of MSC, because of the removal of the forbidden N-shapes in the graph. %Actually, the number of forbidden shapes removed in $\Gamma_{dep}$ is not counted by the algorithm, which applies a general solution (instead of finding each forbidden shape), but it seems that many of them appear.
%The \emph{N-shape}, represented in Figure~\ref{fig:n} is forbidden in a minimal series-parallel graph as it is not possible to exactly express it using sequences and parallel sections. However, a \emph{N-shape} could perfectly be handled by a dynamic scheduler, for example.
Thus, the fact that many \emph{N-shape} are removed in $\Gamma_{dep}$ shows that the creation of a static shedule of tasks may not be the best solution for complex simulations. It has to be noticed, however, that the all computation of $\Gamma_{tsp}$ is still usefull to detect how space loops can be merged in $\Gamma_{data}$.

\subsection{Preliminary Performance Evaluation}
To evaluate performance of the generated component-based parallel structure, we have proceeded as follows. Our current implementation of the MSCAC compiler generates a back-end code using the SkelGIS distributed data structure as an underlying library. For this reason, our evaluation compare the shallow water equations first parallelized with a pure SkelGIS code (data structures, applicators and interfaces of SkelGIS~\cite{CPE:CPE3494}), and second parallelized with MSL (which uses the SkelGIS data structure only). Moreover, as SkelGIS library handles data parallelization for distributed memory architectures, we have limited for now our evaluations to the merged data parallelization of MSCAC (dumped from $\Gamma_{data}$).

>>>>

Figure~\ref{fig:exectime} illustrates the execution time for each step of the MSC transformation for an overall execution time of ten seconds. Execution times have been computed on a laptop with a bi-core Intel Core i5 1.4~GHz, and 8~GB of DDR3. 
One can notice that the transformation of $\Gamma_{dep}$ to a minimal series-parallel graph is the longest step of MSC, because of the removal of the forbidden N-shapes in the graph. %Actually, the number of forbidden shapes removed in $\Gamma_{dep}$ is not counted by the algorithm, which applies a general solution (instead of finding each forbidden shape), but it seems that many of them appear.
%The \emph{N-shape}, represented in Figure~\ref{fig:n} is forbidden in a minimal series-parallel graph as it is not possible to exactly express it using sequences and parallel sections. However, a \emph{N-shape} could perfectly be handled by a dynamic scheduler, for example.
Thus, the fact that many \emph{N-shape} are removed in $\Gamma_{dep}$ shows that the creation of a static schedule of tasks may not be the best solution for complex simulations. It has to be noticed, however, that the all computation of $\Gamma_{tsp}$ is still usefull to detect how space loops can be merged in $\Gamma_{data}$.

%\pagebreak
\subsection{Preliminary Performance Evaluation}
To evaluate performance of the generated component-based parallel structure, we have proceeded as follows. Our current implementation of the MSCAC compiler generates a back-end code using the SkelGIS distributed data structure as an underlying library. For this reason, our evaluation compare the shallow water equations first parallelized with a pure SkelGIS code (data structures, applicators and interfaces of SkelGIS~\cite{CPE:CPE3494}), and second parallelized with MSL (which uses the SkelGIS data structure only). Moreover, as SkelGIS library handles data parallelization for distributed memory architectures, we have limited for now our evaluations to the merged data parallelization of MSCAC (dumped from $\Gamma_{data}$).
